\LARGE How coexistence mechanisms mediate temporal stability

### 2016-02-24 manuscript/manuscript.Rmd
new simulation scripts and results; updates results and figures

```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, fig.height=4.5, fig.width=8, fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (*a,b*) and relative nonlinearity (*c,d*) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their germination fractions are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their germination fractions are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
source("../modelCode/semi_discrete_consumer_resource_fxns.R")

@@

Results
-------

>>>>

```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, fig.height=4.5, fig.width=8, fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (*a,b*) and relative nonlinearity (*c,d*) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their germination fractions are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their germination fractions are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
 ##  Resource uptake function (Hill function)
  uptake_R <- function(r, R, alpha, beta){
    return((r*R^alpha) / (beta^alpha + R^alpha))
  }
  # Get "germination" fractions for each year
  getG <- function(sigE, rho, nTime){
    varcov <- matrix(c(sigE, rho*sigE, rho*sigE, sigE), 2, 2)
    e <- rmvnorm(n = nTime, mean = c(0,0), sigma = varcov)
    g <- exp(e) / (1+exp(e))
    return(g)
  }

@@

Results
-------
Stable coexistence and stable biomass production were positively correlated (rank correlation = #) when species coexistence was maintained by the storage effect.
Species asynchrony decreased as correlations among species' responses to the environmental cue increased (fig. 2a) and the coefficient of variation of total biomass increased (fig. 2b).
These relationships were unaffected by the variance of the resource, but asynchrony and the coefficient of variation of total biomass were always higher at higher levels of resource variability (fig. 2a-b).

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/storage_effect_synchstability}
  \caption{Results from storage effect simulations.}
\end{figure}
